Project-I by Group Sydney

### 2015-10-24 report/paper.tex
pretty print for figures

To separate the data, we have observed that the feature $2$ and $16$ could help us. Figure \ref{fig:feature2}. We can observe $11$ misclassified data (green points), which we will remove them in order to not corrupt our model.  So, this feature can allow us to find the first cluster. For the two others clusters, we need to oberve the feature $16$. Figure \ref{fig:feature16}. We can observe $14$ misclassified data (green points and one blue). They also will be consider as outliers and remove. We set the threshold in order to minimize the number of misclassified data samples. Those thresholds are $0.42$ for the feature $2$ and $1.17$ for the feature $16$. So the final size of our clusters are $1937, 563$ and $273$.

We are also interested about the correlation between the input and output variables. We have observed the correlation for each cluster and conclude that for the first cluster, they are mainly in $[-0.1,0.1]$, except two features which are highly correlated. For the second and third cluster, also mainly in $[-0.1,0.1]$ but this time, there are more correlated features (~15). Moreover, the features seem not have correlation between them.

@@

\begin{figure}[!t]
\center
\subfigure[Histogram of $\mathbf{y}$. We can see three Gaussian distributions and also some outliers on the right.]{\includegraphics[width=2.5in]{figures/histogram.jpg} \label{fig:histogram}}
\hfill
\subfigure[Feature 2, because we have assumed that the data was generated from three Gaussian, this feature can help us to separate the data. Green data points are misclassified data. The separation is at $x=0.42$.]{\includegraphics[width=2.5in]{figures/feature2.jpg}\label{fig:feature2}}
\hfill
\subfigure[Feature 16, because we have assumed that the data was generated from three Gaussian, this feature can help us to separate the data. Green data points are misclassified data. We can see see a blue data point which is misclassified, it will be an outlier. The separation is at $x=1.17$.]{\includegraphics[width=2.5in]{figures/feature16.jpg}\label{fig:feature16}}
\hfill
\caption{}
\end{figure}

@@

Since our matrix is ill-conditioned, using the least squares with normal equation wasn't suitable. Moreover, the results obtained were less good (not so much) compared to the ridge regression method, and so we will not report the results obtained with this method. The method using the least squares with gradient descent was appropriated, but compared to the ridge regression, it was a little bit less efficient and was also much slower to tune correctly the learning step. This is the reason why we will not report the results using this method. Therefore, we have so used the ridge regression method, which is suitable because we should lift the eigenvalues, faster and a little bit more efficient than least squares using gradient descent. Only results obtained with this latter will be reported.

@@

In order to evaluate our different models, we first have split our data ($\mathbf{X}$) in two sets of $80\%$ and $20\%$, for the training and the test sets. We choose this percentage in order to have still enough data for the training set and also enough in order to estimate correctly our models on the testing set with a concrete size. We learn with our models only on the training set and use the test set in order to estimate the error using the \textit{Root Mean Square Error}. Moreover, we have also used k-cross validation (see next section for the values of k) to tune the parameters like lambda of the different polynomial degrees. We repeated the experiment $30$ times with different seed in order to split the data in a unique random way for each trial. Finally, we made varied the lambda from $10^{-5}$ to $10^{5}$ with $500$ values between.

@@

The figure XXX represents the \textit{RMSE} for each models. The first model used in the constant one, which will allow us to compare improvements with others model. It simply returns the mean of the outputs and doesn't depend on the inputs. Our second model does a ridge regression on the overall data using $10$ fold cross validation, because we have a lot of data, splitting them into $10$ fold seems reasonable. As expected, this is much better than previous model because we take into account the input features. Next model is similar to the second one except that we add normalization on the real inputs (it doesn't make sense to also normalize categorical variables). Normalization is generally a good thing and often a necessity depending on the algorithms used (e.g. gradient descent ones). It improves only slightly but because normalization is a good practice, we keep it.

@@

\begin{figure}[!t]
\center
\includegraphics[width=6in]{figures/models.jpg} \label{fig:models}
\caption{Boxplot of our models, using the RMSE. Each model is represented with a box where we can see their mean and their standard deviation.}
\end{figure}

>>>>

To separate the data, we have observed that the feature $2$ and $16$ could help us. With Figure \ref{fig:feature2} we can observe $11$ misclassified data, which we will remove them in order to not corrupt our model.  So, this feature can allow us to find the first cluster. For the two others clusters, we need to oberve the feature $16$. With Figure \ref{fig:feature16}, we can observe $14$ misclassified data. They also will be consider as outliers and remove. We set the threshold in order to minimize the number of misclassified data samples. Those thresholds are $0.42$ for the feature $2$ and $1.17$ for the feature $16$. So the final size of our clusters are $1937, 563$ and $273$.

We are also interested about the correlation between the input and output variables. We have observed the correlation for each cluster and conclude that for the first cluster, they are mainly in $[-0.1,0.1]$, except two features which are highly correlated. For the second and third cluster, also mainly in $[-0.1,0.1]$ but this time, there are more correlated features (around 15). Moreover, the features seem not have correlation between them.

@@

\begin{figure}[!t]
\center
\subfigure[Histogram of $\mathbf{y}$. We can see three Gaussian distributions and also some outliers on the right.]{\includegraphics[width=2.7in]{figures/histogram.jpg} \label{fig:histogram}}
\hfill
\subfigure[Feature 2 can help us to separate the data. Green data points are misclassified data. The separation is at $x=0.42$.]{\includegraphics[width=2.7in]{figures/feature2.jpg}\label{fig:feature2}}
\hfill
\subfigure[Feature 16 can help us to separate the data. Green data points are misclassified data. The separation is at $x=1.17$.]{\includegraphics[width=2.7in]{figures/feature16.jpg}\label{fig:feature16}}
\hfill
\includegraphics[width=6in]{figures/models.jpg} \label{fig:models}
\caption{Boxplot of our models, using the RMSE. Each model is represented with a box where we can see their mean and their standard deviation.}
\caption{}
\end{figure}

@@

Since our matrix is ill-conditioned, using the least squares with normal equation wasn't suitable. Moreover, the results obtained were less good (not so much) compared to the ridge regression method, and so we will not report those. The method using the least squares with gradient descent was appropriated, but compared to the ridge regression, it was a little bit less efficient and was also much slower to tune correctly the learning step. This is the reason why we will not report the results using this method. Therefore, we have so used the ridge regression method, which is suitable because we could lift the eigenvalues in order to avoid ill-conditioned matrix, faster and a little bit more efficient than least squares using gradient descent. Only results obtained with this latter will be reported.

@@

In order to evaluate our different models, we first have split our data ($\mathbf{X}$) in two sets of $80\%$ and $20\%$, for the training and the test sets. We choose this percentage in order to have still enough data for the training set and also enough in order to estimate correctly our models on the testing set with a concrete size. We learn only on the training set and then use the test set in order to estimate the error using the \textit{Root Mean Square Error}. Moreover, we have also used k-cross validation (see next section for the values of k) to tune the parameters up like lambda of the different polynomial degrees. We repeated the experiment $30$ times with different seed in order to split the data in a unique random way for each trial and so . Finally, we made vary the lambda from $10^{-5}$ to $10^{5}$ with $500$ values in-between.

@@

The figure \ref{fig:models} represents the \textit{RMSE} for each models. The first model used in the constant one, which will allow us to compare improvements with others model. It simply returns the mean of the outputs and doesn't depend on the inputs. Our second model does a ridge regression on the overall data using $10$ fold cross validation, because we have a lot of data, splitting them into $10$ fold seems reasonable. As expected, this is much better than previous model because we take into account the input features. Next model is similar to the second one except that we add normalization on the real inputs (it doesn't make sense to also normalize categorical variables). Normalization is generally a good thing and often a necessity depending on the algorithms used (e.g. gradient descent ones). It improves only slightly but because normalization is a good practice, we keep it.

@@
